Next Trippy Structures\thanks{Supported by organization x.}

### 2019-03-07 paper.tex
TTCTR complexities

\newcommand{\acumm}{T-Matrices} % T is for Total!
\newcommand{\ctr}{XCTR}
\newcommand{\ttctr}{TTCTR}
\newcommand{\ctrq}{XCTRc}

@@

\subsection{\ctr}
\label{sec:ctr}
A fundamental weakness of \ttctr~is that it requires several binary search operations over the \texttt{CSA} in the following cases:
\begin{itemize}
    \item We are interested in the number of passengers that started their trip at a stop $s$ and a time window $t_a...t_z$, but from \textbf{any line} (\texttt{start\_X$_{T}$} from Section~\ref{sec:rq}). As $jcodes$ are relative to lines, we must make a separate query for each possible $(s:l_i) \forall l_i \in L$ combinations.
    \item We need to restrict the line of a final stop, in queries such as \texttt{end\_X$_{L}$} or \texttt{from\_X\_to\_Y$_{L}$} (and similar variations). Because the final stops belong to separate entries of the vocabulary that do not encode line identifiers, to restrict a stop $Y\in S$ to a line $l\in L$ we need to search for every possible expanded pattern $W:l,Y...$, for every stop $W$ from the line $l$ that could have been boarded before alighting at $Y$. While it looks tempting to address this issue by modifying the design of \ttctr~so that final stops also encode line identifiers, this would in turn make queries that do not restrict the line of the final stop inefficient, and we would need to perform a new query for every combination of $(s:l_i) \forall l_i \in L$, as in the previous case. \marginpar{\tiny Viendo los experimentos, uno se puede preguntar si no habria quedado mejor meter lineas en paradas finales...}
\end{itemize}

@@

\subsection{Comparing \acumm~and \ctr}
\label{sec:comp}
Better show this after they have been both explained... \marginpar{\tiny Include TTCTR in the table}

\begin{threeparttable}
\centering
\caption{Efficiency of \acumm~and \ctr~against the queries described in Section~\ref{sec:rq}}
\label{tab:queries}
\begin{tabular}{|l|l|l|}
\hline
Query &  \acumm & \ctr\\
\hline
\texttt{board\_X$_{LT}$} & $O(l)$\tnote{a} & \ctrq\tnote{b} \\
\texttt{alight\_X$_{LT}$} & $O(l)$\tnote{a} & Hard\tnote{cd} \\
\texttt{start\_X$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{end\_X$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{switch\_X$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} & - & \ctrq\tnote{b} \\
\texttt{board\_L$_T$} & O(1) & $O(|S| \times \ctrq)$\tnote{be} \\
\texttt{alight\_L$_T$} & O(1) & $O(|S| \times \ctrq)$\tnote{bce} \\
\texttt{start\_L$_T$} & - & $O(log(|L|\times\bar{|J^l|}))$\tnote{fg} \\
\texttt{end\_L$_T$} & - & $O(|S| \times \ctrq)$\tnote{be} \\
\texttt{board\_T} & $O(|L|)$\tnote{f} & Hard\tnote{d} \\
\texttt{alight\_T} & $O(|L|)$\tnote{f} & Hard\tnote{cd} \\
\texttt{start\_T} & - & $O(|L| \times log(|L|\times\bar{|J^l|}))$\tnote{fg}~~ \\
\texttt{end\_T} & - & Hard\tnote{d} \\
\texttt{load\_X$_{LT}$} & $O(l)$\tnote{a} & Hard\tnote{cd} \\
\hline
\end{tabular}

\begin{tablenotes}
\item[a] $l$ is the number of lines we restrict to.
\item[b] The complexity of \ctrq~ varies with the restrictions.
\item[c] May include false positives.
\item[d] Not practical to solve with the indexing capabilities of \ctr.
\item[e] $|S|$ is the number of stops in the line L.
\item[f] $|L|$ is the total number of lines represented.
\item[g] $\bar{|J^l|}$ is the average number of jcodes per line.
\end{tablenotes}
\end{threeparttable}

>>>>

\newcommand{\acumm}{T-Matrices} % T is for Total!
\newcommand{\ctr}{XCTR}
\newcommand{\ttctr}{TTCTR}
\newcommand{\ctrq}{XCTRc}
\newcommand{\ttctrq}{TTCTRc}

@@

\subsection{\ctr}
\label{sec:ctr}
A fundamental weakness of \ttctr~is that it requires several binary search operations over the \texttt{CSA} in the following cases:
\begin{itemize}
    \item We are interested in the number of passengers that started their trip at a stop $s$ and a time window $t_a...t_z$, but from \textbf{any line} (\texttt{start\_X$_{T}$} from Section~\ref{sec:rq}). As $jcodes$ are relative to lines, we must make a separate query for each possible $(s:l_i) \forall l_i \in L$ combination.
    \item We need to restrict the line of a final stop, in queries such as \texttt{end\_X$_{L}$} or \texttt{from\_X\_to\_Y$_{L}$} (and similar variations). Because the final stops belong to separate entries of the vocabulary that do not encode line identifiers, to restrict a stop $Y\in S$ to a line $l\in L$ we need to search for every possible expanded pattern $W:l,Y...$, for every stop $W$ from the line $l$ that could have been boarded before alighting at $Y$. While it looks tempting to address this issue by modifying the design of \ttctr~so that final stops also encode line identifiers, this would in turn make queries that do not restrict the line of the final stop inefficient, and we would need to perform a new query for every combination of $(s:l_i) \forall l_i \in L$, as in the previous case. \marginpar{\tiny Viendo los experimentos, uno se puede preguntar si no habria quedado mejor meter lineas en paradas finales...}
\end{itemize}

@@

\subsection{Comparing \acumm, \ttctr~and \ctr}
\label{sec:comp}
Better show this after they have been both explained...

\begin{threeparttable}
\centering
\caption{Efficiency of \acumm~and \ctr~against the queries described in Section~\ref{sec:rq}}
\label{tab:queries}
\begin{tabular}{|l|l|l|l|}
\hline
Query &  \acumm & \ttctr & \ctr\\
\hline
\texttt{board\_X$_{LT}$} & $O(l)$\tnote{a} & $O(l\times log(\bar{|J^l|}))$\tnote{abg} & \ctrq\tnote{b} \\
\texttt{alight\_X$_{LT}$} & $O(l)$\tnote{a} & Hard\tnote{cd} & Hard\tnote{cd} \\
\texttt{start\_X$_{LT}$} & - & \ttctrq\tnote{b} & \ctrq\tnote{b} \\
\texttt{end\_X$_{LT}$} & - & $O(|S|\times \ttctrq)$\tnote{be} & \ctrq\tnote{b} \\
\texttt{switch\_X$_{LT}$} & - & \ttctrq\tnote{b} & \ctrq\tnote{b} \\
\texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} & - & $O(|S|\times \ttctrq)$\tnote{be} & \ctrq\tnote{b} \\
\texttt{board\_L$_T$} & O(1) & $O(|S|\times log(\bar{|J^l|}))$\tnote{beg} & $O(|S| \times \ctrq)$\tnote{be} \\
\texttt{alight\_L$_T$} & O(1) & $O(|S|\times log(\bar{|J^l|}))$\tnote{bceg} & $O(|S| \times \ctrq)$\tnote{bce} \\
\texttt{start\_L$_T$} & - & $O(|S|\times \ttctrq)$\tnote{be} & $O(log(|L|\times\bar{|J^l|}))$\tnote{fg} \\
\texttt{end\_L$_T$} & - & $O(|S|\times \ttctrq)$\tnote{be}~~~ & $O(|S| \times \ctrq)$\tnote{be} \\
\texttt{board\_T} & $O(|L|)$\tnote{f} & Hard\tnote{d} & Hard\tnote{d} \\
\texttt{alight\_T} & $O(|L|)$\tnote{f} & Hard\tnote{cd} & Hard\tnote{cd} \\
\texttt{start\_T} & - & Hard\tnote{d} & $O(|L| \times log(|L|\times\bar{|J^l|}))$\tnote{fg}~~ \\
\texttt{end\_T} & - & Hard\tnote{d} & Hard\tnote{d} \\
\texttt{load\_X$_{LT}$} & $O(l)$\tnote{a} & Hard\tnote{cd} & Hard\tnote{cd} \\
\hline
\end{tabular}

\begin{tablenotes}
\item[a] $l$ is the number of lines we restrict to.
\item[b] The complexity of varies with the restrictions. See discussion.
\item[c] May include false positives.
\item[d] Not practical to solve with the indexing capabilities of this representation.
\item[e] $|S|$ is the number of stops in the line L.
\item[f] $|L|$ is the total number of lines represented.
\item[g] $\bar{|J^l|}$ is the average number of jcodes per line.
\end{tablenotes}
\end{threeparttable}
